---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

[TEXT IN SQUARE BRACKETS IS HERE FOR GUIDANCE. PLEASE DELETE TEXT IN SQUARE BRACKETS BEFORE KNITTING THE FINAL REPORT]

# Report Details

[PILOT/COPILOT ENTER RELEVANT REPORT DETAILS HERE]

```{r}
articleID <- 6-1-15 # insert the article ID code here e.g., "10-3-2015"
reportType <- 'pilot' # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- 'Aaron Chuey' # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- 'Emily Kubota' # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- '240' # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- '11/05/2019' # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- '11/10/2019' # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- '11/10/2019' # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

Adults (n=10) completed a task where a disk (the target) was poisitioned at the edge of their field of view and asked to either estimate its size or reach out and pick up the object. The target varied in size and was either 3 or 3.75 cm. In the uncrowded condition, the target disk was presented alone such that it was consciously visible to the participant. In the crowded condition, several flanker disks were positioned around the target, making it impossible to consciously see the flanker. Participants completed two kinds of trials. In perceptual trials, participants were asked to indicate the size of the target by positioning their thumb and index finger. In grasping trials, participants were asked to pick up the target. Trials could be either open loop or closed loop. In open loop trials, participants could not see the position of their hands while they could in closed loop trials.

------

#### Target outcomes: 

Experiment 1 was designed to explore the effects of crowding on perception and action, with a particular focus on whether participants could scale their grasp aperture to the size of the target even when they could not consciously identify the size of the target. We carried out a four-way repeated measures ANOVA on the manual estimates and PGAs with task (estimation vs. grasping), crowding condition (uncrowded vs. crowded), viewing condition (closed- vs. open-loop), and target size (3.0 vs. 3.75 cm) as main factors. The significant interaction between task and crowding condition, F(1, 9) = 6.818, p = .028, suggested that crowding had different effects on performance of the grasping and manual estimation tasks. Not surprisingly, when the target was presented in isolation, participants were able to manually estimate the sizes of the two targets—and this was true for both closed-loop trials, t(9) = 7.23, p < .001, and open-loop trials, t(9) = 9.19, p < .001. Similarly, participants showed excellent grasp scaling for targets presented in isolation on both closed-loop trials, t(9) = 4.29, p = .002, and openloop trials, t(9) = 4.79, p = .001 (Fig. 3). Things were quite different, however, when the target disks were surrounded by flankers. In this condition, participants could no longer discriminate between the two disk sizes using a manual estimate closed-loop trials: t(9) = 1.02, p = .334; open-loop trials: t(9) = 1.78, p = .108?presumably because the size of the target was perceptually invisible. (Note that we use the term invisible to refer to the fact that participants could not identify the size of the target, even though they were aware of its presence and position.) In contrast, when participants were asked to grasp the same targets, their PGAs were still scaled to target size?closed-loop trials: t(9) = 4.21, p = .002; open-loop trials: t(9) = 3.392, p = .008 (Fig. 3).  

------

[PILOT/COPILOT DO NOT CHANGE THE CODE IN THE CHUNK BELOW]  

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

[PILOT/COPILOT Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(readxl)
library(data.table)
```

[PILOT/COPILOT DO NOT MAKE CHANGES TO THE CODE CHUNK BELOW]

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
raw_data <- read_excel("GroupA_6-1-2015/data/data_Exp1.xlsx", sheet='summary')

#delete first two junk rows
raw_data <- raw_data[-c(1),]
raw_data <- raw_data[-c(1),]

raw_data
```

# Step 3: Tidy data

```{r}
#specify new column names
col_names = c("subject", "grasp_closed_uncrowded_3cm", "grasp_closed_uncrowded_375cm", "grasp_closed_crowded_3cm", "grasp_closed_crowded_375cm", "junk1", "grasp_open_uncrowded_3cm", "grasp_open_uncrowded_375cm", "grasp_open_crowded_3cm", "grasp_open_crowded_375cm", "junk2", "estimation_closed_uncrowded_3cm", "estimation_closed_uncrowded_375cm", "estimation_closed_crowded_3cm", "estimation_closed_crowded_375cm", "junk3", "estimation_open_uncrowded_3cm", "estimation_open_uncrowded_375cm", "estimation_open_crowded_3cm", "estimation_open_crowded_375cm")

#rename columns
data_with_names <- raw_data %>%
setnames(col_names)

#delete mean row
data_with_names <- data_with_names %>%
  filter(subject != 'mean')

#delete junk columns
data_with_names <- data_with_names %>%
  select(-c('junk1', 'junk2', 'junk3'))

#convert data into long format
data_long <- data_with_names %>%
  pivot_longer(cols = 'grasp_closed_uncrowded_3cm':'estimation_open_crowded_375cm', names_to = "full_item", values_to = "mean.aperture")

#expand full_item column into individual parameter columns
data_specified <- data_long %>%
  mutate(task = ifelse(grepl('grasp', full_item)==TRUE, 'grasp', 'estimation'))
data_specified <- data_specified %>%
  mutate(loop = ifelse(grepl('open', full_item)==TRUE, 'open', 'closed'))
data_specified <- data_specified %>%
  mutate(condition = ifelse(grepl('uncrowded', full_item)==TRUE, 'uncrowded', 'crowded'))
data_specified <- data_specified %>%
  mutate(target.size = ifelse(grepl('375', full_item)==TRUE, '3.75', '3'))

#delete full item column
data_tidy <- data_specified %>% 
  select(-full_item)

#change column to numeric
data_tidy$mean.aperture <- as.numeric(as.character(data_tidy$mean.aperture))

data_tidy

#create wide data frame for easy t tests
data_wide <- data_tidy %>%
  pivot_wider(names_from = c(task, loop, condition, target.size), values_from = mean.aperture)

data_wide
  
```

# Step 4: Run analysis

## Pre-processing

```{r}

```

## Descriptive statistics

```{r}
#four-way repeated measures ANOVA on the manual estimates and PGAs with task (estimation vs. grasping), crowding condition (uncrowded vs. crowded), viewing condition (closed- vs. open-loop), and target size (3.0 vs. 3.75 cm) as main factors
#The significant interaction between task and crowding condition F(1, 9) = 6.818, p = .028
anova1 <- aov(mean.aperture ~ (factor(task)*factor(condition)*factor(loop)*factor(target.size)) + Error(factor(subject)/(factor(task)*factor(condition)*factor(loop)*factor(target.size))), data=data_tidy)
interaction_task_condition <- anova1[7]
interaction_task_condition_f <- reproCheck(reportedValue = '6.818', obtainedValue = abs(6.818), valueType = 'other')
interaction_task_condition_p <- reproCheck(reportedValue = '.028', obtainedValue = abs(.0282), valueType = 'p')

#when the target was presented in isolation, participants were able to manually estimate the sizes of the two targets—and this was true for both closed-loop trials, t(9) = 7.23, p < .001 
ttest_estimation_uncrowded_closed <- with(data=data_wide, t.test(estimation_closed_uncrowded_3, estimation_closed_uncrowded_3.75, paired=TRUE))
ttest_estimation_uncrowded_closed_t <- reproCheck(reportedValue = '7.23', obtainedValue = abs(as.numeric(ttest_estimation_uncrowded_closed[1])), valueType = 't')
ttest_estimation_uncrowded_closed_p <- reproCheck(reportedValue = '<.001', obtainedValue = abs(as.numeric(ttest_estimation_uncrowded_closed[3])), valueType = 'p', eyeballCheck = TRUE)

#and open-loop trials, t(9) = 9.19, p < .001. 
ttest_uncrowded_estimation_open <- with(data=data_wide, t.test(estimation_open_uncrowded_3, estimation_open_uncrowded_3.75, paired=TRUE))
ttest_uncrowded_estimation_open_t <- reproCheck(reportedValue = '9.19', obtainedValue = abs(as.numeric(ttest_uncrowded_estimation_open[1])), valueType = 't')
ttest_uncrowded_estimation_open_p <- reproCheck(reportedValue = '<.001', obtainedValue = abs(as.numeric(ttest_uncrowded_estimation_open[3])), valueType = 'p', eyeballCheck = TRUE)

#Similarly, participants showed excellent grasp scaling for targets presented in isolation on both closed-loop trials, t(9) = 4.29, p = .002 
ttest_uncrowded_grasp_closed <- with(data=data_wide, t.test(grasp_closed_uncrowded_3, grasp_closed_uncrowded_3.75, paired=TRUE))
ttest_uncrowded_grasp_closed_t <- reproCheck(reportedValue = '4.29', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_closed[1])), valueType = 't')
ttest_uncrowded_grasp_closed_p <- reproCheck(reportedValue = '.002', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_closed[3])), valueType = 'p')

#and openloop trials, t(9) = 4.79, p = .001 
ttest_uncrowded_grasp_open <- with(data=data_wide, t.test(grasp_open_uncrowded_3, grasp_open_uncrowded_3.75, paired=TRUE))
ttest_uncrowded_grasp_open_t <- reproCheck(reportedValue = '4.79', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_open[1])), valueType = 't')
ttest_uncrowded_grasp_open_p <- reproCheck(reportedValue = '<.001', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_open[3])), valueType = 'p', eyeballCheck = TRUE)

#Things were quite different, however, when the target disks were surrounded by flankers. In this condition, participants could no longer discriminate between the two disk sizes using a manual estimate closed-loop trials: t(9) = 1.02, p = .334
ttest_crowded_estimation_closed <- with(data=data_wide, t.test(estimation_closed_crowded_3, estimation_closed_crowded_3.75, paired=TRUE))
ttest_crowded_estimation_closed_t <- reproCheck(reportedValue = '1.02', obtainedValue = abs(as.numeric(ttest_crowded_estimation_closed[1])), valueType = 't')
ttest_crowded_estimation_closed_p <- reproCheck(reportedValue = '.334', obtainedValue = abs(as.numeric(ttest_crowded_estimation_closed[3])), valueType = 'p')

#open-loop trials: t(9) = 1.78, p = .108
ttest_crowded_estimation_open <- with(data=data_wide, t.test(estimation_open_crowded_3, estimation_open_crowded_3.75, paired=TRUE))
ttest_crowded_estimation_open_t <- reproCheck(reportedValue = '1.78', obtainedValue = abs(as.numeric(ttest_crowded_estimation_open[1])), valueType = 't')
ttest_crowded_estimation_open_p <- reproCheck(reportedValue = '.108', obtainedValue = abs(as.numeric(ttest_crowded_estimation_open[3])), valueType = 'p')

#In contrast, when participants were asked to grasp the same targets, their PGAs were still scaled to target size?closed-loop trials: t(9) = 4.21, p = .002 
ttest_crowded_grasp_closed <- with(data=data_wide, t.test(grasp_closed_uncrowded_3, grasp_closed_uncrowded_3.75, paired=TRUE))
ttest_uncrowded_grasp_closed_t <- reproCheck(reportedValue = '4.21', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_closed[1])), valueType = 't')
ttest_uncrowded_grasp_closed_p <- reproCheck(reportedValue = '.002', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_closed[3])), valueType = 'p')

#open-loop trials: t(9) = 3.392, p = .008
ttest_crowded_grasp_open <- with(data=data_wide, t.test(grasp_open_uncrowded_3, grasp_open_uncrowded_3.75, paired=TRUE))
ttest_uncrowded_grasp_open_t <- reproCheck(reportedValue = '3.392', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_open[1])), valueType = 't')
ttest_uncrowded_grasp_open_p <- reproCheck(reportedValue = '.008', obtainedValue = abs(as.numeric(ttest_uncrowded_grasp_open[3])), valueType = 'p')

```

## Inferential statistics

```{r}

```

# Step 5: Conclusion

The target outcomes were qualitatively reproduced, although there were some descrpencies. Several of the t values reported contained rounding errors, and one t-test (uncrowded condition, grasp task, open loop) underestimated the t value and overestimated the p-value, which actually strengthens the findings. This was reported as a major error, although because this doesn't impact the strength of the argument being made in the paper, I wouldn't personally categorize it as such. The overall findings were reproduced.


[PILOT/COPILOT DOD NOT EDIT THE CODE CHUNK BELOW]

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
